---
title: "R Notebook"
output: html_notebook
---

```{r}
library(data.table)

library(ggplot2)
theme_set(theme_light())
```

# Loading data



```{r}
hosts = fread("../data/hosts_anonimised.csv")
guests = fread("../data/guests_anonimised.csv")
```


# Actual values

## Hosts gender over time

```{r}
table(hosts$host_since_year, hosts$h_gen)
```

```{r}
hosts_by_year =  hosts[, .(tot_hosts=.N), by=.(host_since_year)]
str(hosts_by_year)
```

```{r}
hosts_gender = merge(
  hosts[, .(.N), by=.(host_since_year, h_gen)],
  hosts_by_year,
  by = "host_since_year"
)

hosts_gender$ratio = hosts_gender$N / hosts_gender$tot_hosts

str(hosts_gender)
```

```{r}
ggplot(hosts_gender[host_since_year>=2012 & host_since_year<2020], aes(x=host_since_year, y=ratio, col=h_gen, label=round(ratio,2))) +
  geom_line(size=.25, linetype="dotted") +
  geom_smooth(se=F, span = 1) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  scale_x_continuous(breaks = 2008:2020) +
  ylim(0,NA) +
  scale_color_hue(l=50)
```


**Take away point**: slight prevalence of female hosts over time. The gap is now smaller.

## Guests gender over time

```{r}
table(guests$guest_since_year, guests$g_gen)
```

```{r}
guests_by_year =  guests[, .(tot_guests=.N), by=.(guest_since_year)]
str(guests_by_year)
```

```{r}
guests_gender = merge(
  guests[, .(.N), by=.(guest_since_year, g_gen)],
  guests_by_year,
  by = "guest_since_year"
)

guests_gender$ratio = guests_gender$N / guests_gender$tot_guests

str(guests_gender)
```


```{r}
ggplot(guests_gender[guest_since_year>=2012 & guest_since_year<2020], aes(x=guest_since_year, y=ratio, col=g_gen, label=round(ratio,2))) +
  geom_line(size=.25, linetype="dotted") +
  geom_smooth(se=F, span = 1) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  scale_x_continuous(breaks = 2008:2020) +
  ylim(0,NA) +
  scale_color_hue(l=50)
```

**Take away point**: slight prevalence of female guests over time. The gap is increasing.


## Hosts age over time

```{r}
table(hosts$host_since_year, hosts$h_age)
```

```{r}
hosts_age = merge(
  hosts[, .(.N), by=.(host_since_year, h_age)],
  hosts_by_year,
  by = "host_since_year"
)

hosts_age$ratio = hosts_age$N / hosts_age$tot_hosts

str(hosts_age)
```

```{r}
ggplot(hosts_age[host_since_year>=2012 & host_since_year<2020], aes(x=host_since_year, y=ratio, col=h_age, label=round(ratio,2))) +
  geom_line(size=.25, linetype="dotted") +
  geom_smooth(se=F, span = 1) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  scale_x_continuous(breaks = 2008:2020) +
  ylim(0,NA) +
  scale_color_hue(l=50)
```

**Take away point**: Prevalence of 30-39 yo in hosts. Over time the 18-29 group increases and the 40+ decreases (in percentage).



# Guest age over time

```{r}
table(guests$guest_since_year, guests$g_age)
```


```{r}
guests_age = merge(
  guests[, .(.N), by=.(guest_since_year, g_age)],
  guests_by_year,
  by = "guest_since_year"
)

guests_age$ratio = guests_age$N / guests_age$tot_guests

str(guests_age)
```

```{r}
ggplot(guests_age[guest_since_year>=2012 & guest_since_year<2020], aes(x=guest_since_year, y=ratio, col=g_age, label=round(ratio,2))) +
  geom_line(size=.25, linetype="dotted") +
  geom_smooth(se=F, span = 1) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  scale_x_continuous(breaks = 2008:2020) +
  ylim(0,NA) +
  scale_color_hue(l=50)
```

**Take away point**: Prevalence of 30-39 yo in guests. Over time the 18-29 group increases and the 40+ decreases (in percentage).


## Hosts ethnicity over time


```{r}
table(hosts$host_since_year, hosts$h_etn)
```

```{r}
hosts_etn = merge(
  hosts[, .(.N), by=.(host_since_year, h_etn)],
  hosts_by_year,
  by = "host_since_year"
)

hosts_etn$ratio = hosts_etn$N / hosts_etn$tot_hosts

str(hosts_etn)
```



```{r}
ggplot(hosts_etn[host_since_year>=2012 & host_since_year<2020], aes(x=host_since_year, y=ratio, col=h_etn, label=round(ratio,2))) +
  geom_line(size=.25, linetype="dotted") +
  geom_smooth(se=F, span = 1) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  scale_x_continuous(breaks = 2008:2020) +
  ylim(0,NA) +
  scale_color_hue(l=50)
```

**Take away point**: White hosts are dominant.. Black community is increasing over time. Other communities (such as hispanic) increasing too.


## Guests ethnicity over time

```{r}
table(guests$guest_since_year, guests$g_etn)
```


```{r}
guests_etn = merge(
  guests[, .(.N), by=.(guest_since_year, g_etn)],
  guests_by_year,
  by = "guest_since_year"
)

guests_etn$ratio = guests_etn$N / guests_etn$tot_guests

str(guests_etn)
```

```{r}
ggplot(guests_etn[guest_since_year>=2012 & guest_since_year<2020], aes(x=guest_since_year, y=ratio, col=g_etn, label=round(ratio,2))) +
  geom_line(size=.25, linetype="dotted") +
  geom_smooth(se=F, span = 1) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  scale_x_continuous(breaks = 2008:2020) +
  ylim(0,NA) +
  scale_color_hue(l=50)
```

**Take away point**: White guests are dominant.. Black community is slightly increasing over time. Asian community has increased too.








# Moving average

## Gender

```{r}
year_back = hosts_gender
year_fut = hosts_gender

year_back$host_since_year = year_back$host_since_year - 1
year_fut$host_since_year = year_fut$host_since_year + 1

semi_j = merge(hosts_gender,
              year_back[, .(host_since_year, h_gen, r_back=ratio)],
              by = c("host_since_year", "h_gen"),
              all.x = T)

h_gen = merge(semi_j,
              year_fut[, .(host_since_year, h_gen, r_fut=ratio)],
              by = c("host_since_year", "h_gen"),
              all.x = T)

h_gen$ratio_avg = rowMeans(h_gen[, .(ratio, r_back, r_fut)], na.rm=TRUE)

remove(year_back, year_fut, semi_j)
```

```{r}
year_back = guests_gender
year_fut = guests_gender

year_back$guest_since_year = year_back$guest_since_year - 1
year_fut$guest_since_year = year_fut$guest_since_year + 1

semi_j = merge(guests_gender,
              year_back[, .(guest_since_year, g_gen, r_back=ratio)],
              by = c("guest_since_year", "g_gen"),
              all.x = T)

g_gen = merge(semi_j,
              year_fut[, .(guest_since_year, g_gen, r_fut=ratio)],
              by = c("guest_since_year", "g_gen"),
              all.x = T)

g_gen$ratio_avg = rowMeans(g_gen[, .(ratio, r_back, r_fut)], na.rm=TRUE)

remove(year_back, year_fut, semi_j)
```

```{r}
h_gen$user = "Host"
g_gen$user = "Guest"

hg_gen = rbind(
  h_gen[, .(year=host_since_year, gender=h_gen, ratio=ratio_avg, user)],
  g_gen[, .(year=guest_since_year, gender=g_gen, ratio=ratio_avg, user)]
)

hg_gen[gender == "female", gender := "Female"]
hg_gen[gender == "male", gender := "Male"]
```


```{r}
p = ggplot(hg_gen[year>=2012 & year<2020], aes(x=year, y=ratio, col=gender, label=round(ratio,2))) +
  geom_line(size=.5) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  facet_wrap( ~ user) +
  scale_x_continuous(breaks = (1:2000)*2) +
  ylim(0,NA) +
  scale_color_hue(l=50) +
  labs(colour = "") +
  theme(legend.position = "bottom")

print(p)

ggsave("gen_year.pdf", plot = p)
```


## Age

```{r}
year_back = hosts_age
year_fut = hosts_age

year_back$host_since_year = year_back$host_since_year - 1
year_fut$host_since_year = year_fut$host_since_year + 1

semi_j = merge(hosts_age,
               year_back[, .(host_since_year, h_age, r_back=ratio)],
               by = c("host_since_year", "h_age"),
               all.x = T)

h_age = merge(semi_j,
              year_fut[, .(host_since_year, h_age, r_fut=ratio)],
              by = c("host_since_year", "h_age"),
              all.x = T)

h_age$ratio_avg = rowMeans(h_age[, .(ratio, r_back, r_fut)], na.rm=TRUE)

remove(year_back, year_fut, semi_j)
```

```{r}
year_back = guests_age
year_fut = guests_age

year_back$guest_since_year = year_back$guest_since_year - 1
year_fut$guest_since_year = year_fut$guest_since_year + 1

semi_j = merge(guests_age,
               year_back[, .(guest_since_year, g_age, r_back=ratio)],
               by = c("guest_since_year", "g_age"),
               all.x = T)

g_age = merge(semi_j,
              year_fut[, .(guest_since_year, g_age, r_fut=ratio)],
              by = c("guest_since_year", "g_age"),
              all.x = T)

g_age$ratio_avg = rowMeans(g_age[, .(ratio, r_back, r_fut)], na.rm=TRUE)

remove(year_back, year_fut, semi_j)
```

```{r}
h_age$user = "Host"
g_age$user = "Guest"

hg_age = rbind(
  h_age[, .(year=host_since_year, age=h_age, ratio=ratio_avg, user)],
  g_age[, .(year=guest_since_year, age=g_age, ratio=ratio_avg, user)]
)
```


```{r}
p = ggplot(hg_age[year>=2012 & year<2020 & age!="0-17"], aes(x=year, y=ratio, col=age, label=round(ratio,2))) +
  geom_line(size=.5) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  facet_wrap( ~ user) +
  scale_x_continuous(breaks = (1:2000)*2 ) +
  ylim(0,NA) +
  scale_color_hue(l=50) +
  labs(colour = "") +
  theme(legend.position = "bottom")

print(p)
ggsave("age_year.pdf", plot = p)
```

## Etn

```{r}
year_back = hosts_etn
year_fut = hosts_etn

year_back$host_since_year = year_back$host_since_year - 1
year_fut$host_since_year = year_fut$host_since_year + 1

semi_j = merge(hosts_etn,
               year_back[, .(host_since_year, h_etn, r_back=ratio)],
               by = c("host_since_year", "h_etn"),
               all.x = T)

h_etn = merge(semi_j,
              year_fut[, .(host_since_year, h_etn, r_fut=ratio)],
              by = c("host_since_year", "h_etn"),
              all.x = T)

h_etn$ratio_avg = rowMeans(h_etn[, .(ratio, r_back, r_fut)], na.rm=TRUE)

remove(year_back, year_fut, semi_j)
```

```{r}
year_back = guests_etn
year_fut = guests_etn

year_back$guest_since_year = year_back$guest_since_year - 1
year_fut$guest_since_year = year_fut$guest_since_year + 1

semi_j = merge(guests_etn,
               year_back[, .(guest_since_year, g_etn, r_back=ratio)],
               by = c("guest_since_year", "g_etn"),
               all.x = T)

g_etn = merge(semi_j,
              year_fut[, .(guest_since_year, g_etn, r_fut=ratio)],
              by = c("guest_since_year", "g_etn"),
              all.x = T)

g_etn$ratio_avg = rowMeans(g_etn[, .(ratio, r_back, r_fut)], na.rm=TRUE)

remove(year_back, year_fut, semi_j)
```

```{r}
h_etn$user = "Host"
g_etn$user = "Guest"

hg_etn = rbind(
  h_etn[, .(year=host_since_year, etn=h_etn, ratio=ratio_avg, user)],
  g_etn[, .(year=guest_since_year, etn=g_etn, ratio=ratio_avg, user)]
)
```


```{r}
p = ggplot(hg_etn[year>=2012 & year<2020], aes(x=year, y=ratio, col=etn, label=round(ratio,2))) +
  geom_line(size=.5) +
  geom_text(check_overlap = TRUE, size=3, col="black", vjust = 0, nudge_y = 0.007) +
  geom_point(size=1) +
  facet_wrap( ~ user) +
  scale_x_continuous(breaks = (1:2000)*2 ) +
  ylim(0,NA) +
  scale_color_hue(l=50) +
  labs(colour = "") +
  theme(legend.position = "bottom")

print(p)
ggsave("etn_year.pdf", plot = p)
```

End!
