---
title: "R Notebook"
output: html_notebook
---

```{r}
library(data.table)
library(irr) # for kappa2 function

library(ggplot2)
theme_set(theme_minimal())

library(ggrepel) # for plots
```

# Preliminary 

Loading data

```{r}
hgr = fread("../Data/host_guests_reviews.csv")
str(hgr)
```

Setting `myloop` rounds of null models

```{r}
myloop = 100
```

Setting some variables useful to control for *location*, *property price* and *room type*.

```{r}
locations = unique( hgr$loc )
prices = unique( hgr$prc )
rooms = unique( hgr$room_type )
```


# Null model for gender

```{r}
# aggregating the actual network
hg_gr_gen = hgr[, .(cnt = .N, 
                    sentiment = mean(compound, na.rm=TRUE),
                    pos = mean(pos, na.rm=TRUE),
                    neu = mean(neu, na.rm=TRUE),
                    neg = mean(neg, na.rm=TRUE)),
                by=.(hg_gen, h_gen, g_gen)]

hg_join_gen = NULL
kappa_scores = NULL
for (i in 1:myloop)
{
  hgr2 = NULL
  for (l in locations) {
    for (p in prices) {
      for (r in rooms){
        #let's randomise each segment
        seg = hgr[loc==l & prc==p & room_type==r]
        
        seg$h_Rgen = seg$h_gen[sample(1:nrow(seg), nrow(seg))]
        seg$g_Rgen = seg$g_gen[sample(1:nrow(seg), nrow(seg))]
        seg$hg_Rgen = paste( tolower(seg$h_Rgen), tolower(seg$g_Rgen), sep="/")
        
        hgr2 = rbind(hgr2, seg)
      }
    }
  }
  
  # kappa agreement score
  # to check if there is agreement between actual and shuffled labels
  df_g_kappa = data.frame(x=hgr2$g_gen, y=hgr2$g_Rgen)
  df_h_kappa = data.frame(x=hgr2$h_gen, y=hgr2$h_Rgen)
  df_kappa = rbind(df_g_kappa, df_h_kappa)
  kappa_scores = append( kappa_scores, kappa2(df_kappa)$value )

  # aggregating the null network
  hg_Rgr_gen = hgr2[, .(rnd = .N, 
                       Rsentiment = mean(compound, na.rm=TRUE),
                       Rpos = mean(pos, na.rm=TRUE),
                       Rneu = mean(neu, na.rm=TRUE),
                       Rneg = mean(neg, na.rm=TRUE)),
                   by=.(hg_Rgen, h_Rgen, g_Rgen)]
  
  # computing preferential attachment and gain sentiment
  hg_Tjoin_gen = merge(hg_gr_gen, hg_Rgr_gen, by.x="hg_gen", by.y="hg_Rgen")
  hg_Tjoin_gen[, p_attch := cnt/rnd - 1]
  hg_Tjoin_gen[, gain_sentiment := sentiment/Rsentiment - 1]
  hg_Tjoin_gen[, gain_pos := pos/Rpos - 1]
  hg_Tjoin_gen[, gain_neu := neu/Rneu - 1]
  hg_Tjoin_gen[, gain_neg := neg/Rneg - 1]
  hg_Tjoin_gen$iteration = i
  
  hg_join_gen = rbind(hg_join_gen, hg_Tjoin_gen)
  remove(hg_Rgr_gen, hg_Tjoin_gen)
}

hist(kappa_scores)
```



Visualisation: using box-plots so clearly see quartiles

```{r}
ggplot(hg_join_gen, aes(x=p_attch)) +
  geom_vline(xintercept = 0, col="lightblue", size=1) +
  geom_boxplot(size=.25, fill="gray90", alpha=.5, outlier.shape = 1) +
  facet_grid( paste("Host -", h_gen) ~ paste("Guest -", g_gen) ) +
  xlab("preferential attachment") + ylab("guests") +
  scale_x_continuous(breaks = -10:10/10, limits = c(-.15, .15))
```

Visualisation: tile plot, more compact


```{r}
hg_gen = hg_join_gen[, 
                     .(attach_m = median(p_attch),
                       attach_05 = quantile(p_attch, probs = .05),
                       attach_q1 = quantile(p_attch, probs = .25),
                       attach_q3 = quantile(p_attch, probs = .75),
                       attach_95 = quantile(p_attch, probs = .95),
                       gain_sentiment = median(gain_sentiment),
                       gain_pos = median(gain_pos),
                       gain_neu = median(gain_neu),
                       gain_neg = median(gain_neg)),
                     by=.(g_gen, h_gen)]
str(hg_gen)
```

Possible shapes: 4, 15, 18, 21, 23

```{r}
p = ggplot(hg_gen, aes(x=attach_m, y=g_gen, label=round(attach_m,2))) +
  facet_wrap( ~ paste("Host:", h_gen)) +
  geom_vline(xintercept = 0, col="gray", size=1.5) +
  geom_col(width = 0.02, col="gray", fill="gray") +
  geom_point(size=3) +
  geom_text(size=4, vjust = -1) +
  #scale_color_gradient(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-.45,.45)) +
  #scale_x_continuous(limits = c(-0.2,NA), breaks=(-5:5)/5) +
  ylab("Guest") + xlab("Preferential Attachment")

print(p)
```



```{r}
hg_gen$hg_gen = paste0(hg_gen$h_gen, "/", hg_gen$g_gen)

p = ggplot(hg_gen, aes(x=attach_m, y=reorder(hg_gen, attach_m), fill=attach_m, col=attach_m, label=round(attach_m,2))) +
  geom_vline(xintercept = 0, col="black", size=1) +
  geom_col(width = 0.05) +
  geom_point(size=4) +
  geom_point(aes(x=(attach_05)), size=3, shape=3, col="black") +
  geom_point(aes(x=(attach_95)), size=3, shape=3, col="black") +
  geom_text(size=4, vjust = -1, col="black") +
  scale_color_gradient2(low = "darkred", high="forestgreen", mid="white", midpoint = 0, limits=c(-.06,.06)) +
  scale_fill_gradient2(low = "darkred", high="forestgreen", mid="white", midpoint = 0, limits=c(-.06,.06)) +
  theme(legend.position = "none") +
  ylab("Host / Guest") + xlab("Preferential Attachment")

print(p)
ggsave("pa_gen.pdf", plot = p, width = 5, height = 4)
```



```{r}
hg_gen[, attach_disp := attach_m]
hg_gen[attach_m>-0.03 & attach_m<0.03, attach_disp := 0]
hg_gen[attach_m>0.45, attach_disp := 0.45]

p = ggplot(hg_gen, aes(x=g_gen, y=h_gen, fill=attach_disp)) +
  scale_fill_gradient2(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-.45,.45)) +
  geom_tile(color = "white", lwd = 3, linetype = 1) +
  geom_text(aes(label = paste("q1:", round(attach_q1,2)) ), color = "gray30", size = 3, vjust=-2) +
  geom_text(aes(label = round(attach_m,2)), color = "black", size = 4) +
  geom_text(aes(label = paste("q3:", round(attach_q3,2)) ), color = "gray30", size = 3, vjust=3) +
  labs(fill="pa") +
  xlab("guests") + ylab("hosts") 

print(p)
#ggsave("pa_gen.pdf", plot = p, width = 3.5, height = 3.5)
```




# Null model for age

```{r}
# aggregating the actual network
hg_gr_age = hgr[, .(cnt = .N, 
                    sentiment = mean(compound, na.rm=TRUE),
                    pos = mean(pos, na.rm=TRUE),
                    neu = mean(neu, na.rm=TRUE),
                    neg = mean(neg, na.rm=TRUE)),
                by=.(hg_age, h_age, g_age)]

hg_join_age = NULL
kappa_scores = NULL
for (i in 1:myloop)
{
  hgr2 = NULL
  for (l in locations) {
    for (p in prices) {
      for (r in rooms){
        #let's randomise each segment
        seg = hgr[loc==l & prc==p & room_type==r]
        
        seg$h_Rage = seg$h_age[sample(1:nrow(seg), nrow(seg))]
        seg$g_Rage = seg$g_age[sample(1:nrow(seg), nrow(seg))]
        seg$hg_Rage = paste( tolower(seg$h_Rage), tolower(seg$g_Rage), sep="/")
        
        hgr2 = rbind(hgr2, seg)
      }
    }
  }
  
  # kappa agreement score
  # to check if there is agreement between actual and shuffled labels
  df_g_kappa = data.frame(x=hgr2$g_age, y=hgr2$g_Rage)
  df_h_kappa = data.frame(x=hgr2$h_age, y=hgr2$h_Rage)
  df_kappa = rbind(df_g_kappa, df_h_kappa)
  kappa_scores = append( kappa_scores, kappa2(df_kappa)$value )

  # aggregating the null network
  hg_Rgr_age = hgr2[, .(rnd = .N, 
                       Rsentiment = mean(compound, na.rm=TRUE),
                       Rpos = mean(pos, na.rm=TRUE),
                       Rneu = mean(neu, na.rm=TRUE),
                       Rneg = mean(neg, na.rm=TRUE)),
                   by=.(hg_Rage, h_Rage, g_Rage)]
  
  # computing preferential attachment and gain sentiment
  hg_Tjoin_age = merge(hg_gr_age, hg_Rgr_age, by.x="hg_age", by.y="hg_Rage")
  hg_Tjoin_age[, p_attch := cnt/rnd - 1]
  hg_Tjoin_age[, gain_sentiment := sentiment/Rsentiment - 1]
  hg_Tjoin_age[, gain_pos := pos/Rpos - 1]
  hg_Tjoin_age[, gain_neu := neu/Rneu - 1]
  hg_Tjoin_age[, gain_neg := neg/Rneg - 1]
  hg_Tjoin_age$iteration = i
  
  hg_join_age = rbind(hg_join_age, hg_Tjoin_age)
  remove(hg_Rgr_age, hg_Tjoin_age)
}

hist(kappa_scores)
```


```{r}
ggplot(hg_join_age, aes(x=p_attch)) +
  geom_vline(xintercept = 0, col="lightblue", size=1) +
  geom_boxplot(size=.25, fill="gray90", alpha=.5, outlier.shape = 1) +
  facet_grid( paste("Host -", h_age) ~ paste("Guest -", g_age) ) +
  xlab("preferential attachment") + ylab("guests") +
  scale_x_continuous(breaks = -10:10/10, limits = c(-.15, .15))
```


```{r}
hg_age = hg_join_age[, 
                     .(attach_m = median(p_attch),
                       attach_05 = quantile(p_attch, probs = .05),
                       attach_q1 = quantile(p_attch, probs = .25),
                       attach_q3 = quantile(p_attch, probs = .75),
                       attach_95 = quantile(p_attch, probs = .95),
                       gain_sentiment = median(gain_sentiment),
                       gain_pos = median(gain_pos),
                       gain_neu = median(gain_neu),
                       gain_neg = median(gain_neg)),
                     by=.(g_age, h_age)]
str(hg_age)
```

```{r}
p = ggplot(hg_age, aes(x=attach_m, y=g_age, label=round(attach_m,2))) +
  facet_wrap( ~ paste("Host:", h_age)) +
  geom_vline(xintercept = 0, col="gray", size=1.5) +
  geom_col(col="gray", fill="gray", width = 0.02) +
  geom_point(size=3, col="orange") +
  geom_text(size=4, vjust = -1) +
  #scale_x_continuous(limits = c(-0.2,NA), breaks=(-5:5)/5) +
  ylab("Guest") + xlab("Preferential Attachment")

print(p)
```



```{r}
hg_age$hg_age = paste0(hg_age$h_age, "/", hg_age$g_age)

p = ggplot(hg_age, aes(x=(attach_m), y=reorder(hg_age, attach_m), fill=attach_m, col=attach_m, label=round(attach_m,2))) +
  geom_vline(xintercept = 0, col="black", size=1) +
  geom_col(width = 0.1) +
  geom_point(size=4) +
  geom_point(aes(x=(attach_05)), size=3, shape=3, col="black") +
  geom_point(aes(x=(attach_95)), size=3, shape=3, col="black") +
  geom_text(size=4, vjust = -1, col="black") +
  scale_color_gradient2(low = "darkred", high="forestgreen", mid="white", midpoint = 0, limits=c(-.12,.12)) +
  scale_fill_gradient2(low = "darkred", high="forestgreen", mid="white", midpoint = 0, limits=c(-.12,.12)) +
  theme(legend.position = "none") +
  ylab("Host / Guest") + xlab("Preferential Attachment")

print(p)
ggsave("pa_age.pdf", plot = p, width = 5, height = 4)
```



```{r}
hg_age[, attach_disp := attach_m]
hg_age[attach_m>-0.03 & attach_m<0.03, attach_disp := 0]
hg_age[attach_m>0.45, attach_disp := 0.45]

p = ggplot(hg_age, aes(x=g_age, y=h_age, fill=attach_disp)) +
  scale_fill_gradient2(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-.45,.45)) +
  geom_tile(color = "white", lwd = 3, linetype = 1) +
  geom_text(aes(label = paste("q1:", round(attach_q1,2)) ), color = "gray30", size = 3, vjust=-2) +
  geom_text(aes(label = round(attach_m,2)), color = "black", size = 4) +
  geom_text(aes(label = paste("q3:", round(attach_q3,2)) ), color = "gray30", size = 3, vjust=3) +
  labs(fill="pa") +
  xlab("guests") + ylab("hosts") 

print(p)
#ggsave("pa_age.pdf", plot = p, width = 3.5, height = 3.5)
```


# Null model for ethnicity 

```{r}
# aggregating the actual network
hg_gr_etn = hgr[, .(cnt = .N, 
                    sentiment = mean(compound, na.rm=TRUE),
                    pos = mean(pos, na.rm=TRUE),
                    neu = mean(neu, na.rm=TRUE),
                    neg = mean(neg, na.rm=TRUE)),
                by=.(hg_etn, h_etn, g_etn)]

hg_join_etn = NULL
kappa_scores = NULL
for (i in 1:myloop)
{
  hgr2 = NULL
  for (l in locations) {
    for (p in prices) {
      for (r in rooms){
        #let's randomise each segment
        seg = hgr[loc==l & prc==p & room_type==r]
        
        seg$h_Retn = seg$h_etn[sample(1:nrow(seg), nrow(seg))]
        seg$g_Retn = seg$g_etn[sample(1:nrow(seg), nrow(seg))]
        seg$hg_Retn = paste( tolower(seg$h_Retn), tolower(seg$g_Retn), sep="/")
        
        hgr2 = rbind(hgr2, seg)
      }
    }
  }

  # kappa agreement score
  # to check if there is agreement between actual and shuffled labels
  df_g_kappa = data.frame(x=hgr2$g_etn, y=hgr2$g_Retn)
  df_h_kappa = data.frame(x=hgr2$h_etn, y=hgr2$h_Retn)
  df_kappa = rbind(df_g_kappa, df_h_kappa)
  kappa_scores = append( kappa_scores, kappa2(df_kappa)$value )  
  
  # aggregating the null network
  hg_Rgr_etn = hgr2[, .(rnd = .N, 
                       Rsentiment = mean(compound, na.rm=TRUE),
                       Rpos = mean(pos, na.rm=TRUE),
                       Rneu = mean(neu, na.rm=TRUE),
                       Rneg = mean(neg, na.rm=TRUE)),
                   by=.(hg_Retn, h_Retn, g_Retn)]
  
  # computing preferential attachment and gain sentiment
  hg_Tjoin_etn = merge(hg_gr_etn, hg_Rgr_etn, by.x="hg_etn", by.y="hg_Retn")
  hg_Tjoin_etn[, p_attch := cnt/rnd - 1]
  hg_Tjoin_etn[, gain_sentiment := sentiment/Rsentiment - 1]
  hg_Tjoin_etn[, gain_pos := pos/Rpos - 1]
  hg_Tjoin_etn[, gain_neu := neu/Rneu - 1]
  hg_Tjoin_etn[, gain_neg := neg/Rneg - 1]
  hg_Tjoin_etn$iteration = i
  
  hg_join_etn = rbind(hg_join_etn, hg_Tjoin_etn)
  remove(hg_Rgr_etn, hg_Tjoin_etn)
}

hist(kappa_scores)
```


```{r}
ggplot(hg_join_etn, aes(x=p_attch)) +
  geom_vline(xintercept = 0, col="lightblue", size=1) +
  geom_boxplot(size=.25, fill="gray90", alpha=.5, outlier.shape = 1) +
  facet_grid( paste("Host -", h_etn) ~ paste("Guest -", g_etn) ) +
  xlab("preferential attachment") + ylab("guests") +
  scale_x_continuous(breaks = -10:10/2, limits = c(-1.5, 1.5))
```


```{r}
hg_etn = hg_join_etn[, 
                     .(attach_m = median(p_attch),
                       attach_05 = quantile(p_attch, probs = .05),
                       attach_q1 = quantile(p_attch, probs = .25),
                       attach_q3 = quantile(p_attch, probs = .75),
                       attach_95 = quantile(p_attch, probs = .95),
                       gain_sentiment = median(gain_sentiment),
                       gain_pos = median(gain_pos),
                       gain_neu = median(gain_neu),
                       gain_neg = median(gain_neg)),
                     by=.(g_etn, h_etn)]
str(hg_etn)
```

```{r}
p = ggplot(hg_etn, aes(x=attach_m, y=g_etn, label=round(attach_m,2))) +
  facet_wrap( ~ paste("Host:", h_etn)) +
  geom_vline(xintercept = 0, col="gray", size=1.5) +
  geom_col(col="gray", fill="gray", width = 0.05) +
  geom_point(size=3, col="orange") +
  geom_text(size=4, vjust = -1) +
  scale_x_continuous(limits = c(-0.2,NA), breaks=(-5:5)/5) +
  ylab("Guest") + xlab("Preferential Attachment")


print(p)
```


```{r}
hg_etn$hg_etn = paste0(hg_etn$h_etn, "/", hg_etn$g_etn)

p = ggplot(hg_etn[abs(attach_m)>0.05], aes(x=attach_m, y=reorder(hg_etn, attach_m), 
                                           fill=sign(attach_m)*abs(attach_m)^(1/2), 
                                           col=sign(attach_m)*abs(attach_m)^(1/2), 
                                           label=round(attach_m,2))) +
  geom_vline(xintercept = 0, col="black", size=1) +
  geom_col(width = 0.1) +
  geom_point(size=4) +
  geom_point(aes(x=(attach_05)), size=3, shape=3, col="black") +
  geom_point(aes(x=(attach_95)), size=3, shape=3, col="black") +
  geom_text(size=4, vjust = -1, col="black") +
  scale_color_gradient2(low = "darkred", high="forestgreen", mid="white", midpoint = 0, limits=c(-1.1,1.1)) +
  scale_fill_gradient2(low = "darkred", high="forestgreen", mid="white", midpoint = 0, limits=c(-1.1,1.1)) +
  theme(legend.position = "none") +
  scale_x_continuous(limits = c(-0.2,NA), breaks=(-5:5)/5) +
  ylab("Host / Guest") + xlab("Preferential Attachment")

print(p)
ggsave("pa_etn.pdf", plot = p, width = 5, height = 4)
```

```{r}
hg_etn[, attach_disp := attach_m]
hg_etn[attach_m>-0.03 & attach_m<0.03, attach_disp := 0]
hg_etn[attach_m>0.45, attach_disp := 0.45]

p = ggplot(hg_etn, aes(x=g_etn, y=h_etn, fill=attach_disp)) +
  scale_fill_gradient2(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-.45,.45)) +
  geom_tile(color = "white", lwd = 3, linetype = 1) +
  geom_text(aes(label = paste("q1:", round(attach_q1,2)) ), color = "gray30", size = 3, vjust=-2) +
  geom_text(aes(label = round(attach_m,2)), color = "black", size = 4) +
  geom_text(aes(label = paste("q3:", round(attach_q3,2)) ), color = "gray30", size = 3, vjust=3) +
  labs(fill="pa") +
  xlab("guests") + ylab("hosts") 

print(p)
#ggsave("pa_gen.pdf", plot = p, width = 3.5, height = 3.5)
```


# Combining all together (age, gender, ethnicity)

Binding all aggregated data (from age, gender, ethnicity)

```{r}
hg_all = rbind(hg_age[, .(guest=g_age, host=h_age, pa=attach_m, gain_comp=gain_sentiment, gain_pos, gain_neu, gain_neg, gr="age")], 
               hg_etn[, .(guest=g_etn, host=h_etn, pa=attach_m, gain_comp=gain_sentiment, gain_pos, gain_neu, gain_neg, gr="etn")],
               hg_gen[, .(guest=g_gen, host=h_gen, pa=attach_m, gain_comp=gain_sentiment, gain_pos, gain_neu, gain_neg, gr="gen")])

str(hg_all)
```
Simplifying the notation

```{r}
hg_all[guest=="18-29", guest:="18"]
hg_all[guest=="30-39", guest:="30"]
hg_all[guest=="40+", guest:="40"]

hg_all[guest=="Asian", guest:="A"]
hg_all[guest=="Black", guest:="B"]
hg_all[guest=="White", guest:="W"]
hg_all[guest=="Others", guest:="O"]

hg_all[guest=="female", guest:="F"]
hg_all[guest=="male", guest:="M"]

table(hg_all$guest)
```


```{r}
hg_all[host=="18-29", host:="18"]
hg_all[host=="30-39", host:="30"]
hg_all[host=="40+", host:="40"]

hg_all[host=="Asian", host:="A"]
hg_all[host=="Black", host:="B"]
hg_all[host=="White", host:="W"]
hg_all[host=="Others", host:="O"]

hg_all[host=="Female", host:="F"]
hg_all[host=="Male", host:="M"]

table(hg_all$host)
```

```{r}
hg_all$homophily = "false"
hg_all[guest==host, homophily := "true"]
```








```{r}
ggplot(hg_all, aes(x=pa, y=(gain_pos))) +
  geom_vline(xintercept = 0, col="lightblue", size=.5) +
  geom_hline(yintercept = 0, col="lightblue", size=.5) +
  geom_point(aes(col=gr, shape=homophily), fill=2, size=3) +
  scale_shape_manual(values=c(1, 16)) +
  geom_text_repel(aes( label=paste(guest, host, sep="/") ), color = "black", size = 3) +
  labs(col="group") +
  xlab("preferential attachment") + ylab("gain in positive score") +
  scale_x_continuous(breaks = -10:10/20, limits = c(-.15, .15)) +
  scale_y_continuous(breaks = -10:10/20, limits = c(-.1, .1))
```

```{r}
ggplot(hg_all, aes(x=pa, y=(gain_neu))) +
  geom_vline(xintercept = 0, col="lightblue", size=.5) +
  geom_hline(yintercept = 0, col="lightblue", size=.5) +
  geom_point(aes(col=gr, shape=homophily), fill=2, size=3) +
  scale_shape_manual(values=c(1, 16)) +
  geom_text_repel(aes( label=paste(guest, host, sep="/") ), color = "black", size = 3) +
  labs(col="group") +
  xlab("preferential attachment") + ylab("gain in neutral score") +
  scale_x_continuous(breaks = -10:10/20, limits = c(-.15, .15)) +
  scale_y_continuous(breaks = -10:10/20, limits = c(-.1, .1))
```

```{r}
ggplot(hg_all, aes(x=pa, y=(gain_neg))) +
  geom_vline(xintercept = 0, col="lightblue", size=.5) +
  geom_hline(yintercept = 0, col="lightblue", size=.5) +
  geom_point(aes(col=gr, shape=homophily), fill=2, size=3) +
  scale_shape_manual(values=c(1, 16)) +
  geom_text_repel(aes( label=paste(guest, host, sep="/") ), color = "black", size = 3) +
  labs(col="group") +
  xlab("preferential attachment") + ylab("gain in negative score") +
  scale_x_continuous(breaks = -10:10/20, limits = c(-.15, .15)) +
  scale_y_continuous(breaks = -10:10/20, limits = c(-.1, .1))
```

```{r}
p = ggplot(hg_all, aes(x=pa, y=(gain_comp+0.01))) +
  geom_vline(xintercept = 0, col="lightblue", size=.5) +
  geom_hline(yintercept = 0, col="lightblue", size=.5) +
  geom_point(aes(col=gr, shape=homophily), fill=2, size=3) +
  scale_shape_manual(values=c(1, 16)) +
  geom_text_repel(aes( label=paste(guest, host, sep="/") ), color = "black", size = 3) +
  labs(col="group") +
  xlab("preferential attachment") + ylab("sentiment gain") +
  scale_x_continuous(breaks = -10:10/20, limits = c(-.15, .15)) +
  scale_y_continuous(breaks = -10:10/20, limits = c(-.15, .15))

print(p)
#ggsave("sent_vs_pa.pdf", plot = p)
```


```{r}
ggplot(hg_all, aes(x=rank(pa), y=(gain_comp+0.01))) +
  geom_hline(yintercept = 0, col="lightblue", size=.5) +
  geom_point(aes(col=gr, shape=homophily), fill=2, size=3) +
  scale_shape_manual(values=c(1, 16)) +
  geom_text_repel(aes( label=paste(guest, host, sep="/") ), color = "black", size = 3) +
  labs(col="group") +
  xlab("rank of preferential attachment") + ylab("gain in sentiment") +
  scale_y_continuous(breaks = -10:10/20, limits = c(-.1, .1))
```

```{r}
cor.test(hg_all$pa, hg_all$gain_comp, method="spearman")
```


```{r}
hg_gen$sent = hg_gen$gain_sentiment + 0.01
hg_gen[, sentiment_disp := sent]
hg_gen[sent>-0.019 & sent<0.019, sentiment_disp := 0]

hg_gen[g_gen == "male", g_gen := "Male"]
hg_gen[g_gen == "female", g_gen := "Female"]

p = ggplot(hg_gen, aes(x=g_gen, y=h_gen, fill = sentiment_disp )) +
  scale_fill_gradient2(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-0.45, 0.45)) +
  geom_tile(color = "white", lwd = 3, linetype = 1) +
  geom_text(aes(label = round(sent,2)), color = "black", size = 3) +
  labs(fill="sent_gain") +
  xlab("guests") + ylab("hosts") +
  theme(legend.position = "none")

print(p)
#ggsave("sent_gen.pdf", plot = p, width = 3.5, height = 3.5)
```

```{r}
hg_age$sent = hg_age$gain_sentiment + 0.01
hg_age[, sentiment_disp := sent]
hg_age[sent>-0.019 & sent<0.019, sentiment_disp := 0]

p = ggplot(hg_age, aes(x=g_age, y=h_age, fill = sentiment_disp )) +
  scale_fill_gradient2(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-0.45, 0.45)) +
  geom_tile(color = "white", lwd = 3, linetype = 1) +
  geom_text(aes(label = round(sent,2)), color = "black", size = 3) +
  labs(fill="sent_gain") +
  xlab("guests") + ylab("hosts") +
  theme(legend.position = "none")

print(p)
#ggsave("sent_age.pdf", plot = p, width = 3.5, height = 3.5)
```

```{r}
hg_etn$sent = hg_etn$gain_sentiment + 0.01
hg_etn[, sentiment_disp := sent]
hg_etn[sent>-0.017 & sent<0.017, sentiment_disp := 0]

p = ggplot(hg_etn, aes(x=g_etn, y=h_etn, fill = sentiment_disp )) +
  scale_fill_gradient2(low = "orange", high="forestgreen", mid="white", midpoint = 0, limits=c(-0.45, 0.45)) +
  geom_tile(color = "white", lwd = 3, linetype = 1) +
  geom_text(aes(label = round(sent,2)), color = "black", size = 3) +
  labs(fill="sent_gain") +
  xlab("guests") + ylab("hosts") +
  theme(legend.position = "note")

print(p)
#ggsave("sent_etn.pdf", plot = p, width = 3.5, height = 3.5)
```



```{r}
ggplot(hgr, aes(x=pos)) +
  geom_histogram(aes(y = ..density..), bins = 100, fill="cyan4") +
  geom_density() 
```

```{r}
ggplot(hgr, aes(x=neu)) +
  geom_histogram(aes(y = ..density..), bins = 100, fill="cyan4") +
  geom_density() 
```

```{r}
ggplot(hgr, aes(x=neg)) +
  geom_histogram(aes(y = ..density..), bins = 100, fill="cyan4") +
  geom_density() 
```

```{r}
ggplot(hgr, aes(x=compound)) +
  geom_histogram(aes(y = ..density..), bins = 100, fill="cyan4") +
  geom_density() 
```



End!
